### 2022-03-17 Articulo1_LIDE_UsoDelTiempo_ChristianJavierSalasMarquez.Rmd
Construcción del primer artículo para LIDE. Uso del tiempo.

---
title: "Uso del tiempo de los ecuatorianos"
author: "Christian Salas Marquez"
date: "2022-03-17"
output: html_notebook
---

```{r}
###############################################################
####                   Descargar los datos                 ####
###############################################################

if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(haven)) install.packages("haven", repos = "http://cran.us.r-project.org")
if(!require(readr)) install.packages("readr", repos = "http://cran.us.r-project.org")

```