### 2022-04-30 Articulo3_LIDE/AnalisisExploratorio_REMD_2019.Rmd
Conexión con las bases de datos.

---
title: "Análisis Exploratorio REMD 2019"
author: "Christian Javier Salas Marquez"
date: '2022'
output:
  html_document:
    df_print: paged
---

```{r}
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(haven)) install.packages("haven", repos = "http://cran.us.r-project.org")
if(!require(readr)) install.packages("readr", repos = "http://cran.us.r-project.org")
```

```{r}
EMA_2019 <- read.csv2("https://raw.githubusercontent.com/christianjaviersalasmarquez/LIDE_ESPOL_Christian_Salas/main/Articulo3_LIDE/REMD_2019/EMA_2019.csv")

EDV_2019 <- read.csv2("https://raw.githubusercontent.com/christianjaviersalasmarquez/LIDE_ESPOL_Christian_Salas/main/Articulo3_LIDE/REMD_2019/EDV_2019.csv")
```